Teaching modeling in introductory statistics: A comparison of formula and tidyverse syntaxes

### 2023-01-13 PaperDraft.Rmd
run styler on paper code

```{r setup, include=FALSE}
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})

knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, out.width = "80%", fig.asp = 0.618, fig.align = "center", time_it = FALSE, comment="")
here::i_am("PaperDraft.Rmd")
library(kableExtra)
options(knitr.kable.NA = "", ggplot2.discrete.fill = c("#64baaa", "#154e56"), ggplot2.discrete.colour = c("#64baaa", "#154e56"))

@@

# Some code to add chunk captions
library(knitr)
chunk_hook = knit_hooks$get("chunk")
knit_hooks$set(chunk = function(x, options) {
  x = chunk_hook(x, options)
  if(!is.null(options$codecap))
    x = paste0(x, "\n\\captionof{chunk}{", options$codecap,"}\n")
  if(!is.null(options$ref))
    x = paste0(x, "\n\\label{", options$ref,"}\n")

  # Based on https://stackoverflow.com/questions/53887473/how-can-i-control-fontsize-and-linestretch-of-code-chunks-independently-from-the
  code_space = 1
  text_space = 2

  paste0(
    "\\linespread{", code_space,"}\n", 
    x,
    "\\linespread{", text_space,"}\n",
    "\\vspace{3mm}\\setlength{\\parindent}{15pt}"
  )
})
```

@@

```{r data-load, cache = FALSE}
youtube_weeks <- read_csv(here("data", "processed", "youtube_weeks.csv"), col_types = cols(
  week = col_double(),
  section = col_character(),
  n_videos = col_double(),
  watches = col_double(),
  uniques = col_double(),
  hours = col_double(),
  tot_length = col_double(),
  tot_min = col_double(),
  mpu = col_double(),
  mps = col_double(),
  percent_per_student = col_double(),
  percent_per_user= col_double()
))

@@

prepostsurvey <- prepostsurvey %>%
  slice(-1) %>%
   mutate(Section.x = case_when(
     Section.x == "202040STAT220-01 and 202040STAT220-52" ~ "formula",
     Section.x == "202040STAT220-01 and 202040STAT220-53" ~ "tidyverse"
   ),
   Section.y = case_when(
     Section.y == "202040STAT220-01 and 202040STAT220-52" ~ "formula",
     Section.y == "202040STAT220-01 and 202040STAT220-53" ~ "tidyverse"
   ))

@@

```{r}
labsfortesting <- lablines %>%
  drop_na(file) %>%
  pivot_wider(week, names_from = section, values_from = lines) %>%
  mutate(diff = tidyverse - formula,
         perc_diff = (diff/formula)*100) %>%
  drop_na(week)
```

@@

youtube_videos %>%
  mutate(week = case_when(section == "formula" ~  week - 0.15,
                          section == "tidyverse" ~ week + 0.25)) %>%
  ggplot(aes(x = week, y = tot_min, fill = section)) +
  geom_col(position = "stack", color = "white", width = 0.4) +
  scale_x_continuous(breaks = seq(from = , to = 15, by = 2)) +
  # facet_wrap(~section, nrow = 2) +
  ylab("Total length of pre-lab \n videos (minutes)") +
  xlab("Week of semester") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.y = element_text(size = 14)
  )
```

@@

```{r}
youtube_fortesting <- youtube_weeks %>%
  select(week, section, tot_min) %>%
  pivot_wider(week, names_from = section, values_from = tot_min) %>%
  mutate(diff = tidyverse - formula, 
         avglength = (tidyverse + formula)/2, 
         perc_diff = (diff/formula)*100)
```

@@

pre_sum <- pre_sum %>%
  drop_na(feeling) %>%
  group_by(Section, skill, feeling) %>%
  summarize(n = n()) %>%
  mutate(prop = n/sum(n)) %>%
  select(-n) %>%
  mutate(type = "pre")

post_sum <- prepostsurvey %>%
  select(Section.y, Q11.y:Q16.y) %>%
  drop_na(Section.y) %>%
  pivot_longer(-Section.y, names_to = "skill", 
                 values_to = "feeling") %>%
  rename(Section = Section.y)

post_sum <- post_sum %>%
  drop_na(feeling) %>%
  group_by(Section, skill, feeling) %>%
  summarize(n = n()) %>%
  mutate(prop = n/sum(n)) %>%
  select(-n) %>%
  mutate(type = "post")

prepost_sum <- pre_sum %>%
  bind_rows(post_sum) %>%
  mutate(type = as_factor(type)) %>%
  mutate(type = fct_relevel(type, "post", "pre")) %>%
  mutate(skill = str_remove_all(skill, ".[xy]"))%>%
  mutate(skill = as_factor(skill)) %>%
  mutate(skill = fct_rev(fct_relevel(skill, "Q12", "Q13", "Q14", "Q15", "Q16", "Q11"))) %>%
  mutate(skill = fct_recode(skill, 
                            "Programming Efficient" = "Q13",
                            "Raw Data" = "Q12",
                            "Analyses Easier" = "Q15",
                            "Search Online" = "Q16",
                            "Overcome Problem" = "Q14",
                            "Programming Confident" = "Q11"))

@@

prepost_neu <- prepost_sum %>%
  filter(feeling == "3 - neutral") %>%
  mutate(prop = prop/2)

@@

```{r pre-post, fig.cap = "Pre- and post-survey responses to Likert-scale questions. Most questions show some level of improvement, such as the first question, `I am confident in my ability to make use of programming software to work with data.' but others show no change or even a decline in agreement.", out.width = "95%", fig.asp = 1}
likert_palette <- c("1 - strongly disagree" = "#a6611a", "2" = "#dfc27d", "3 - neutral" = "grey90", "4" = "#80cdc1", "5 - strongly agree" = "#018571")
prepost_pos %>%
ggplot(aes(x=type, y=prop, fill = feeling)) + 
  geom_col() +
  geom_col(data=prepost_neg) +
  coord_flip() +
  facet_nested(rows = vars(skill, Section), switch = "y", 
               strip = strip_nested(size = "variable"),
               labeller = labeller(skill = label_wrap_gen(width = 10))) +
  theme_bw() + 
  theme(strip.placement = "outside") +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    text = element_text(size = 15),
    strip.text.y.left = element_text(angle = 0, size = 8),
    panel.spacing.y = unit(c(rep(c(2,5), times = 5), 2), "mm")
  ) +
  xlab("") +
  ylab("Percentage") +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(from=-1, to = 1, by = 0.5), labels = c(100, 50, 0, 50, 100)) +
  scale_fill_manual(values = likert_palette) 
```

@@

```{r}
pre_paired <- prepostsurvey %>%
  select(Section.x, Q11.x:Q16.x, Section.y, Q11.y:Q16.y) %>%
  drop_na() %>%
  mutate(across(contains("Q"), parse_number)) %>%
  mutate(Q11 = Q11.y - Q11.x,
         Q12 = Q12.y - Q12.x,
         Q13 = Q13.y - Q13.x,
         Q14 = Q14.y - Q14.x,
         Q15 = Q15.y - Q15.x,
         Q16 = Q16.y - Q16.x) %>%
  rename(Section = Section.x) %>%
  select(Section, Q11:Q16) %>%
  pivot_longer(-Section, names_to = "skill", values_to = "diff")

prepost_joined <- pre_paired %>%
  mutate(skill = fct_recode(skill,
    "Programming Efficient" = "Q13",
    "Raw Data" = "Q12",
    "Analyses Easier" = "Q15",
    "Search Online" = "Q16",
    "Overcome Problem" = "Q14",
    "Programming Confident" = "Q11"
  )) %>%
  mutate(skill = fct_relevel(skill, "Programming Confident", "Search Online", "Analyses Easier", "Overcome Problem","Programming Efficient", "Raw Data"))
```

@@

```{r post-sentiment, fig.cap = "Responses to the question, ``How was the experience of learning to program in R?''"}
prepostsurvey %>%
  mutate(Q23 = as_factor(Q23)) %>%
  mutate(Q23 = fct_relevel(Q23, "About what I expected -- in a good way", "Not what I expected -- in a good way", "About what I expected -- in a bad way", "Not what I expected -- in a bad way")) %>%
  mutate(Q23 = fct_recode(Q23, "About what I expected -- \n in a good way" = "About what I expected -- in a good way", "Not what I expected -- \n in a good way" = "Not what I expected -- in a good way", "About what I expected -- \n in a bad way" = "About what I expected -- in a bad way", "Not what I expected -- \n in a bad way" = "Not what I expected -- in a bad way")) %>%
  drop_na(Q23) %>%
  rename(Section = Section.y) %>%
  group_by(Section, Q23) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Q23, y = prop, fill = Section), position = position_dodge2(preserve = "single", reverse = TRUE, padding = 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_discrete() +
  # facet_wrap(~Section) +
  ylab("") +
  xlab("") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 1), aspect.ratio = 2/3,
        axis.text.y=element_text(hjust=0)) +
  ggtitle("How was the experience of learning to program in R?") +
    theme(
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

@@

```{r rstudio-hours, fig.cap="Hours of compute time per student over the course of the semester. Lines connect within students, to follow within-student variability."}
rstudio_cloud <- rstudio_cloud %>%
  mutate(month = as_factor(month))%>%
  mutate(month_num = case_when(month == "September" ~ 0, 
                               month == "October" ~ 1, 
                               month == "November" ~ 2,
                               month == "December" ~ 3))
# ggplot(rstudio_cloud) +
#   geom_boxplot(aes(y = amount, x = section)) +
#   facet_grid(~ rev(month)) +
#   ylab("Hours of compute time on RStudio Cloud") +
#   xlab("") +
#   theme(
#     legend.position = "bottom",
#     legend.title = element_blank()
#   )

@@

```{r}
overallmean <- rstudio_cloud %>%
  group_by(section) %>%
  summarize(mean=round(mean(amount), digits = 1)) %>%
  pivot_wider(names_from = section, values_from = mean)
```

@@

```{r meancompute, results='asis'}
options(knitr.kable.NA = "missing")
rstudio_cloud %>%
  group_by(section, month) %>%
  summarize(mean = round(mean(amount), digits = 1), 
            sd = round(sd(amount), digits = 1)) %>%
  mutate(info = paste0(mean, " (", sd, ")")) %>%
  select(section, info, month) %>%
  pivot_wider(names_from = month, values_from = info) %>%
  kable(caption = "Mean student compute time on RStudio Cloud per month in hours (standard deviation in parentheses), broken down by section. Note different months had different numbers of assignments, although the number of assignments was consistent between sections.", booktabs = TRUE)
options(knitr.kable.NA = "")
```

@@

topics2 <- topics2 %>%
  mutate(month = case_when(week < 4 ~ "September",
                           week >= 4 & week < 9 ~ "October",
                           week >=9 & week < 13 ~ "November",
                           week >= 13 ~ "December"))

@@

options(knitr.kable.NA = "missing")
rstudio_cloud %>%
  group_by(section, month) %>%
  summarize(mean = mean(amount)) %>%
  left_join(topics2) %>%
  mutate(approx_per = round(mean/n, digits =2)) %>%
  select(section, month, approx_per) %>%
  pivot_wider(names_from = section, values_from = approx_per) %>%
  mutate(diff = tidyverse - formula, mins = diff*60) %>%
  mutate(difference = ifelse(is.na(diff), NA, paste0(diff, " (", round(mins), " minutes)"))) %>% 
  mutate(formula = as.character(formula), tidyverse = as.character(tidyverse)) %>%
  select(month:tidyverse, difference) %>%
  pivot_longer(-month, names_to = "section", values_to = "num") %>%
  pivot_wider(names_from = month, values_from = num) %>%
  kable(caption = "Approximate time per assignment on RStudio Cloud per month in hours, broken down by section. For this crude approximation, we have divided each month's average by the number of assignments due in the month. (September: 2, October: 5, November: 3, December: 5.) The difference between the section is also computed, and converted into minutes.", booktabs = TRUE)
options(knitr.kable.NA = "")
```

@@

```{r functionsummary, results='asis'}
 num_reused <- allfunctions %>%
  group_by(section) %>%
  summarize(n_fun = n(), reused = sum(n>1), prop = round(sum(n>1)/n(), 2)*100)

num_reused %>%
  mutate(prop = paste0(prop, "%")) %>%
  kable(col.names=c("Section", "Number of functions", "Number used \nmore than once", "Proportion of \n functions reused"), caption = "Number of functions used in each section, including the number used more than once and the proportion reused.", align = "l", booktabs = TRUE) %>%
  column_spec(2:4, width = "1.5in")
```

@@

```{r}
p_tidyverse_functions <- allfunctions %>%
  filter(n > 2, section == "tidyverse") %>%
  mutate(text = fct_reorder(text, n)) %>%
  mutate(text = fct_relevel(text, "library", after = Inf)) %>%
  slice_max(order_by = n, n = 15) %>%
  ggplot() + 
  geom_vline(xintercept = 10)+
  geom_col(aes(y=text, x=n), fill = "#154e56") + 
  xlim(0, 35) +
  labs(title = "tidyverse", x = "", y = "")
```

```{r}
p_formula_functions <- allfunctions %>%
  filter(n > 2, section == "formula") %>%
  mutate(text = fct_reorder(text, n)) %>%
  slice_max(order_by = n, n = 15) %>%
  ggplot() + 
  geom_vline(xintercept = 10)+
  geom_col(aes(y=text, x=n), fill = "#64baaa") + 
  xlim(0, 35) +
  labs(title = "formula", x="", y="")
```

@@

```{r}
tidytotalfunctions <- nrow(tidyfunctions_unique) + nrow(bothfunctions)
formulatotalfunctions <- nrow(formulafunctions_unique)+ nrow(bothfunctions)
```

>>>>

```{r setup, include=FALSE}
knitr::knit_hooks$set(document = function(x) {
  sub("\\usepackage[]{color}", "\\usepackage{xcolor}", x, fixed = TRUE)
})

knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, out.width = "80%", fig.asp = 0.618, fig.align = "center", time_it = FALSE, comment = "")
here::i_am("PaperDraft.Rmd")
library(kableExtra)
options(knitr.kable.NA = "", ggplot2.discrete.fill = c("#64baaa", "#154e56"), ggplot2.discrete.colour = c("#64baaa", "#154e56"))

@@

# Some code to add chunk captions
library(knitr)
chunk_hook <- knit_hooks$get("chunk")
knit_hooks$set(chunk = function(x, options) {
  x <- chunk_hook(x, options)
  if (!is.null(options$codecap)) {
    x <- paste0(x, "\n\\captionof{chunk}{", options$codecap, "}\n")
  }
  if (!is.null(options$ref)) {
    x <- paste0(x, "\n\\label{", options$ref, "}\n")
  }

  # Based on https://stackoverflow.com/questions/53887473/how-can-i-control-fontsize-and-linestretch-of-code-chunks-independently-from-the
  code_space <- 1
  text_space <- 2

  paste0(
    "\\linespread{", code_space, "}\n",
    x,
    "\\linespread{", text_space, "}\n",
    "\\vspace{3mm}\\setlength{\\parindent}{15pt}"
  )
})
```

@@

```{r data-load, cache = FALSE}
youtube_weeks <- read_csv(here("data", "processed", "youtube_weeks.csv"), col_types = cols(
  week = col_double(),
  section = col_character(),
  n_videos = col_double(),
  watches = col_double(),
  uniques = col_double(),
  hours = col_double(),
  tot_length = col_double(),
  tot_min = col_double(),
  mpu = col_double(),
  mps = col_double(),
  percent_per_student = col_double(),
  percent_per_user = col_double()
))

@@

prepostsurvey <- prepostsurvey %>%
  slice(-1) %>%
  mutate(
    Section.x = case_when(
      Section.x == "202040STAT220-01 and 202040STAT220-52" ~ "formula",
      Section.x == "202040STAT220-01 and 202040STAT220-53" ~ "tidyverse"
    ),
    Section.y = case_when(
      Section.y == "202040STAT220-01 and 202040STAT220-52" ~ "formula",
      Section.y == "202040STAT220-01 and 202040STAT220-53" ~ "tidyverse"
    )
  )

@@

```{r}
labsfortesting <- lablines %>%
  drop_na(file) %>%
  pivot_wider(week, names_from = section, values_from = lines) %>%
  mutate(
    diff = tidyverse - formula,
    perc_diff = (diff / formula) * 100
  ) %>%
  drop_na(week)
```

@@

youtube_videos %>%
  mutate(week = case_when(
    section == "formula" ~ week - 0.15,
    section == "tidyverse" ~ week + 0.25
  )) %>%
  ggplot(aes(x = week, y = tot_min, fill = section)) +
  geom_col(position = "stack", color = "white", width = 0.4) +
  scale_x_continuous(breaks = seq(from = , to = 15, by = 2)) +
  # facet_wrap(~section, nrow = 2) +
  ylab("Total length of pre-lab \n videos (minutes)") +
  xlab("Week of semester") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.y = element_text(size = 14)
  )
```

@@

```{r}
youtube_fortesting <- youtube_weeks %>%
  select(week, section, tot_min) %>%
  pivot_wider(week, names_from = section, values_from = tot_min) %>%
  mutate(
    diff = tidyverse - formula,
    avglength = (tidyverse + formula) / 2,
    perc_diff = (diff / formula) * 100
  )
```

@@

pre_sum <- pre_sum %>%
  drop_na(feeling) %>%
  group_by(Section, skill, feeling) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  mutate(type = "pre")

post_sum <- prepostsurvey %>%
  select(Section.y, Q11.y:Q16.y) %>%
  drop_na(Section.y) %>%
  pivot_longer(-Section.y,
    names_to = "skill",
    values_to = "feeling"
  ) %>%
  rename(Section = Section.y)

post_sum <- post_sum %>%
  drop_na(feeling) %>%
  group_by(Section, skill, feeling) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  mutate(type = "post")

prepost_sum <- pre_sum %>%
  bind_rows(post_sum) %>%
  mutate(type = as_factor(type)) %>%
  mutate(type = fct_relevel(type, "post", "pre")) %>%
  mutate(skill = str_remove_all(skill, ".[xy]")) %>%
  mutate(skill = as_factor(skill)) %>%
  mutate(skill = fct_rev(fct_relevel(skill, "Q12", "Q13", "Q14", "Q15", "Q16", "Q11"))) %>%
  mutate(skill = fct_recode(skill,
    "Programming Efficient" = "Q13",
    "Raw Data" = "Q12",
    "Analyses Easier" = "Q15",
    "Search Online" = "Q16",
    "Overcome Problem" = "Q14",
    "Programming Confident" = "Q11"
  ))

@@

prepost_neu <- prepost_sum %>%
  filter(feeling == "3 - neutral") %>%
  mutate(prop = prop / 2)

@@

```{r pre-post, fig.cap = "Pre- and post-survey responses to Likert-scale questions. Most questions show some level of improvement, such as the first question, `I am confident in my ability to make use of programming software to work with data.' but others show no change or even a decline in agreement.", out.width = "95%", fig.asp = 1}
likert_palette <- c("1 - strongly disagree" = "#a6611a", "2" = "#dfc27d", "3 - neutral" = "grey90", "4" = "#80cdc1", "5 - strongly agree" = "#018571")
prepost_pos %>%
  ggplot(aes(x = type, y = prop, fill = feeling)) +
  geom_col() +
  geom_col(data = prepost_neg) +
  coord_flip() +
  facet_nested(
    rows = vars(skill, Section), switch = "y",
    strip = strip_nested(size = "variable"),
    labeller = labeller(skill = label_wrap_gen(width = 10))
  ) +
  theme_bw() +
  theme(strip.placement = "outside") +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    text = element_text(size = 15),
    strip.text.y.left = element_text(angle = 0, size = 8),
    panel.spacing.y = unit(c(rep(c(2, 5), times = 5), 2), "mm")
  ) +
  xlab("") +
  ylab("Percentage") +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(from = -1, to = 1, by = 0.5), labels = c(100, 50, 0, 50, 100)) +
  scale_fill_manual(values = likert_palette)
```

@@

```{r}
pre_paired <- prepostsurvey %>%
  select(Section.x, Q11.x:Q16.x, Section.y, Q11.y:Q16.y) %>%
  drop_na() %>%
  mutate(across(contains("Q"), parse_number)) %>%
  mutate(
    Q11 = Q11.y - Q11.x,
    Q12 = Q12.y - Q12.x,
    Q13 = Q13.y - Q13.x,
    Q14 = Q14.y - Q14.x,
    Q15 = Q15.y - Q15.x,
    Q16 = Q16.y - Q16.x
  ) %>%
  rename(Section = Section.x) %>%
  select(Section, Q11:Q16) %>%
  pivot_longer(-Section, names_to = "skill", values_to = "diff")

prepost_joined <- pre_paired %>%
  mutate(skill = fct_recode(skill,
    "Programming Efficient" = "Q13",
    "Raw Data" = "Q12",
    "Analyses Easier" = "Q15",
    "Search Online" = "Q16",
    "Overcome Problem" = "Q14",
    "Programming Confident" = "Q11"
  )) %>%
  mutate(skill = fct_relevel(skill, "Programming Confident", "Search Online", "Analyses Easier", "Overcome Problem", "Programming Efficient", "Raw Data"))
```

@@

```{r post-sentiment, fig.cap = "Responses to the question, ``How was the experience of learning to program in R?''"}
prepostsurvey %>%
  mutate(Q23 = as_factor(Q23)) %>%
  mutate(Q23 = fct_relevel(Q23, "About what I expected -- in a good way", "Not what I expected -- in a good way", "About what I expected -- in a bad way", "Not what I expected -- in a bad way")) %>%
  mutate(Q23 = fct_recode(Q23, "About what I expected -- \n in a good way" = "About what I expected -- in a good way", "Not what I expected -- \n in a good way" = "Not what I expected -- in a good way", "About what I expected -- \n in a bad way" = "About what I expected -- in a bad way", "Not what I expected -- \n in a bad way" = "Not what I expected -- in a bad way")) %>%
  drop_na(Q23) %>%
  rename(Section = Section.y) %>%
  group_by(Section, Q23) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot() +
  geom_col(aes(x = Q23, y = prop, fill = Section), position = position_dodge2(preserve = "single", reverse = TRUE, padding = 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_discrete() +
  # facet_wrap(~Section) +
  ylab("") +
  xlab("") +
  coord_flip() +
  theme(
    plot.title = element_text(hjust = 1), aspect.ratio = 2 / 3,
    axis.text.y = element_text(hjust = 0)
  ) +
  ggtitle("How was the experience of learning to program in R?") +
  theme(
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

@@

```{r rstudio-hours, fig.cap="Hours of compute time per student over the course of the semester. Lines connect within students, to follow within-student variability."}
rstudio_cloud <- rstudio_cloud %>%
  mutate(month = as_factor(month)) %>%
  mutate(month_num = case_when(
    month == "September" ~ 0,
    month == "October" ~ 1,
    month == "November" ~ 2,
    month == "December" ~ 3
  ))
# ggplot(rstudio_cloud) +
#   geom_boxplot(aes(y = amount, x = section)) +
#   facet_grid(~ rev(month)) +
#   ylab("Hours of compute time on RStudio Cloud") +
#   xlab("") +
#   theme(
#     legend.position = "bottom",
#     legend.title = element_blank()
#   )

@@

```{r}
overallmean <- rstudio_cloud %>%
  group_by(section) %>%
  summarize(mean = round(mean(amount), digits = 1)) %>%
  pivot_wider(names_from = section, values_from = mean)
```

@@

```{r meancompute, results='asis'}
options(knitr.kable.NA = "missing")
rstudio_cloud %>%
  group_by(section, month) %>%
  summarize(
    mean = round(mean(amount), digits = 1),
    sd = round(sd(amount), digits = 1)
  ) %>%
  mutate(info = paste0(mean, " (", sd, ")")) %>%
  select(section, info, month) %>%
  pivot_wider(names_from = month, values_from = info) %>%
  kable(caption = "Mean student compute time on RStudio Cloud per month in hours (standard deviation in parentheses), broken down by section. Note different months had different numbers of assignments, although the number of assignments was consistent between sections.", booktabs = TRUE)
options(knitr.kable.NA = "")
```

@@

topics2 <- topics2 %>%
  mutate(month = case_when(
    week < 4 ~ "September",
    week >= 4 & week < 9 ~ "October",
    week >= 9 & week < 13 ~ "November",
    week >= 13 ~ "December"
  ))

@@

options(knitr.kable.NA = "missing")
rstudio_cloud %>%
  group_by(section, month) %>%
  summarize(mean = mean(amount)) %>%
  left_join(topics2) %>%
  mutate(approx_per = round(mean / n, digits = 2)) %>%
  select(section, month, approx_per) %>%
  pivot_wider(names_from = section, values_from = approx_per) %>%
  mutate(diff = tidyverse - formula, mins = diff * 60) %>%
  mutate(difference = ifelse(is.na(diff), NA, paste0(diff, " (", round(mins), " minutes)"))) %>%
  mutate(formula = as.character(formula), tidyverse = as.character(tidyverse)) %>%
  select(month:tidyverse, difference) %>%
  pivot_longer(-month, names_to = "section", values_to = "num") %>%
  pivot_wider(names_from = month, values_from = num) %>%
  kable(caption = "Approximate time per assignment on RStudio Cloud per month in hours, broken down by section. For this crude approximation, we have divided each month's average by the number of assignments due in the month. (September: 2, October: 5, November: 3, December: 5.) The difference between the section is also computed, and converted into minutes.", booktabs = TRUE)
options(knitr.kable.NA = "")
```

@@

```{r functionsummary, results='asis'}
num_reused <- allfunctions %>%
  group_by(section) %>%
  summarize(n_fun = n(), reused = sum(n > 1), prop = round(sum(n > 1) / n(), 2) * 100)

num_reused %>%
  mutate(prop = paste0(prop, "%")) %>%
  kable(col.names = c("Section", "Number of functions", "Number used \nmore than once", "Proportion of \n functions reused"), caption = "Number of functions used in each section, including the number used more than once and the proportion reused.", align = "l", booktabs = TRUE) %>%
  column_spec(2:4, width = "1.5in")
```

@@

```{r}
p_tidyverse_functions <- allfunctions %>%
  filter(n > 2, section == "tidyverse") %>%
  mutate(text = fct_reorder(text, n)) %>%
  mutate(text = fct_relevel(text, "library", after = Inf)) %>%
  slice_max(order_by = n, n = 15) %>%
  ggplot() +
  geom_vline(xintercept = 10) +
  geom_col(aes(y = text, x = n), fill = "#154e56") +
  xlim(0, 35) +
  labs(title = "tidyverse", x = "", y = "")
```

```{r}
p_formula_functions <- allfunctions %>%
  filter(n > 2, section == "formula") %>%
  mutate(text = fct_reorder(text, n)) %>%
  slice_max(order_by = n, n = 15) %>%
  ggplot() +
  geom_vline(xintercept = 10) +
  geom_col(aes(y = text, x = n), fill = "#64baaa") +
  xlim(0, 35) +
  labs(title = "formula", x = "", y = "")
```

@@

```{r}
tidytotalfunctions <- nrow(tidyfunctions_unique) + nrow(bothfunctions)
formulatotalfunctions <- nrow(formulafunctions_unique) + nrow(bothfunctions)
```
